RILS-ROLS: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-10-12 doc/paper.tex
Reorganized varcnt plots.

\begin{center}
	\begin{tikzpicture}
		\begin{axis}[
			xlabel=$variable\;count$,
			ylabel=$exact\;percentage$,
			xmin=0, xmax=6,
			ymin=0, ymax=100,
			xtick={1,2,3,4,5},
			xticklabels={1,2,3,4,5},   % <---
			ytick={0,10,...,100}
			]
			\addplot[smooth,mark=*,blue] plot coordinates {
				(1,52.31)
				(2,50)
				(3,44)
				(4,37.78)
				(5,13.33)
			};
			\addlegendentry{No noise}

			\addplot[smooth,color=red,mark=x]
			plot coordinates {
				(1,16.92)
				(2,21.67)
				(3,28)
				(4,17.78)
				(5,6.67)
			};
			\addlegendentry{Noise level 0.001}

			\addplot[smooth,color=green,mark=o]
			plot coordinates {
				(1,9.23)
				(2,15)
				(3,12)
				(4,11.11)
				(5,6.67)
			};
			\addlegendentry{Noise level 0.01}
		\end{axis}
	\end{tikzpicture}
	\captionof{figure}{Exact solution percentages for varying levels of noise and variable counts}
	\label{fig:compExact_noise_varcnt}
\end{center}

\begin{center}
	\begin{tikzpicture}
		\begin{axis}[
			xlabel=$variable\;count$,
			ylabel=$exact\;percentage$,
			xmin=0, xmax=6,
			ymin=0, ymax=100,
			xtick={1,2,3,4,5},
			xticklabels={1,2,3,4,5},   % <---
			ytick={0,10,...,100}
			]
			\addplot[smooth,mark=*,blue] plot coordinates {
				(1,86.15)
				(2,75)
				(3,72)
				(4,48.89)
				(5,40)
			};
			\addlegendentry{No noise}

			\addplot[smooth,color=red,mark=x]
			plot coordinates {
				(1,64.62)
				(2,66.67)
				(3,62)
				(4,40)
				(5,40)
			};
			\addlegendentry{Noise level 0.001}

			\addplot[smooth,color=green,mark=o]
			plot coordinates {
				(1,32.31)
				(2,43.33)
				(3,46)
				(4,24.44)
				(5,13.33)
			};
			\addlegendentry{Noise level 0.01}
		\end{axis}
	\end{tikzpicture}
	\captionof{figure}{Percentages of solutions having $R^2 > 0.999$ for varying levels of noise and variable counts}
	\label{fig:compR2_noise_varcnt}
\end{center}

>>>>

\begin{center}
	\begin{tikzpicture}
		\begin{axis}[
			xlabel=$variable\;count$,
			ylabel=$exact\;percentage$,
			xmin=0, xmax=5,
			ymin=0, ymax=100,
			xtick={1,2,3,4},
			xticklabels={1,2,3,4},   % <---
			ytick={0,10,...,100}
			]
			\addplot[smooth,mark=*,blue] plot coordinates {
				(1,43.33)
				(2,43.33)
				(3,46.67)
				(4,46.67)
			};
			\addlegendentry{No noise}

			\addplot[smooth,color=red,mark=x]
			plot coordinates {
				(1,3.33)
				(2,3.33)
				(3,26.67)
				(4,26.67)
			};
			\addlegendentry{Noise level 0.001}

			\addplot[smooth,color=green,mark=o]
			plot coordinates {
				(1,3.33)
				(2,3.33)
				(3,3.33)
				(4,16.67)
			};
			\addlegendentry{Noise level 0.01}
		\end{axis}
	\end{tikzpicture}
	\captionof{figure}{Exact solution percentages for varying levels of noise and variable counts (only sizes ranging from 7 to 12)}
	\label{fig:compExact_noise_varcnt}
\end{center}

\begin{center}
	\begin{tikzpicture}
		\begin{axis}[
			xlabel=$variable\;count$,
			ylabel=$exact\;percentage$,
			xmin=0, xmax=5,
			ymin=0, ymax=100,
			xtick={1,2,3,4},
			xticklabels={1,2,3,4},   % <---
			ytick={0,10,...,100}
			]
			\addplot[smooth,mark=*,blue] plot coordinates {
				(1,83.33)
				(2,66.67)
				(3,73.33)
				(4,46.67)
			};
			\addlegendentry{No noise}

			\addplot[smooth,color=red,mark=x]
			plot coordinates {
				(1,56.67)
				(2,63.33)
				(3,66.67)
				(4,46.67)
			};
			\addlegendentry{Noise level 0.001}

			\addplot[smooth,color=green,mark=o]
			plot coordinates {
				(1,23.33)
				(2,43.33)
				(3,53.33)
				(4,26.67)
			};
			\addlegendentry{Noise level 0.01}
		\end{axis}
	\end{tikzpicture}
	\captionof{figure}{Percentages of solutions having $R^2 > 0.999$ for varying levels of noise and variable counts (only sizes ranging from 7 to 12)}
	\label{fig:compR2_noise_varcnt}
\end{center}
